Semi-supervised author disambiguation for large and partially annotated databases of scientific publications

### 2015-07-14 paper.tex
abstract

\title{Semi-supervised author disambiguation for large and partially annotated databases of scientific publications}
\author{Gilles Louppe, Hussein Al-Natsheh and Mateusz Susik\\
       \it{CERN, Geneva, Switzerland}}

\date{}

%\icmltitlerunning{Semi-supervised author disambiguation for large and partially annotated databases of scientific publications}

@@

Author name disambiguation in bibliographic databases is the problem of
grouping together scientific publications written by a same person. This
problem is difficult because (i) an author may use different spellings,
variants or synonyms across her career and/or (ii) distinct authors may share
the same name. Among solutions ot this problem, digital libraries are
increasingly offering tools for authors to manually curate their publications
and claim which ones are theirs. Indirectly, these tools allow for the
inexpensive collection of large annotated training data that can be further
leveraged to improve the overall accuracy of the system. In this context, we
propose a semi-supervised machine learning disambiguation solution in the case
large and partially annotated databases of scientific publications. We describe
how this annotated data can be used to learn an accurate classifier for
identifying corefering authors, guide the clustering of scientific publications
by distinct authors and finally match the resulting clusters to existing
profiles. Evaluation is carried out on a real-world database of 1 million
annotated publications and demonstrates the very good accuracy of the proposed
solution. In particular, our analysis of parameters and features reveal that...
\glnote{To be completed with actual results.}

>>>>

\title{Semi-supervised author disambiguation for large and partially annotated databases of scientific publications}
\author{Gilles Louppe, Hussein Al-Natsheh and Mateusz Susik\\
       \it{CERN, Geneva, Switzerland}}
\date{}

@@

Author name disambiguation in bibliographic databases is the problem of
grouping together scientific publications written by a same person. This
problem is difficult because (i) an author may use different spellings,
variants or synonyms across her career and/or (ii) distinct authors may share
the same name. Among solutions ot this problem, digital libraries are
increasingly offering tools for authors to manually curate their publications
and claim which ones are theirs. Indirectly, these tools allow for the
inexpensive collection of large annotated training data, which can be further
leveraged to build an automated disambiguation system generalizing to
unlabelled publications. In this context, we propose a semi-supervised machine
learning disambiguation solution in the case large and partially annotated
databases of scientific publications. We describe how this annotated data can
be used to learn an accurate classifier for identifying corefering authors,
guide the clustering of scientific publications by distinct authors and finally
match the resulting clusters to existing profiles. Evaluation is carried out on
a real-world database of 1 million manual annotations and demonstrates the
very good accuracy of the proposed solution. In particular, our analysis of
parameters and features reveal that... \glnote{To be completed with actual
results.}
